---
title: "Tutorial R, lets practice!"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## About package *learnr*

> Create interactive tutorials using R Markdown. Use a combination of narrative, figures, videos, exercises, and quizzes to create self-paced tutorials for learning about R and R packages.

## Basic Mathematics Operations

- Addition
- Subtraction
- Multiplication
- Division

### Exercise 1

Make some calculations and check the answers.

```{r addition, exercise=TRUE}
1 + 1
```

## R Datasets

### Exercise 2

Select an other R database and use the function **str()** to visualization of structure of data.

```{r answer, exercise=TRUE}
datasets::iris
str(iris)
```

## Vector Position

### Exercise 3
 
```{r question, echo=FALSE}
  question("What number is the letter A in the *English* alphabet?",
    answer("8"),
    answer("14"),
    answer("1", correct = TRUE),
    answer("23")
  )
```

## Importing Data

### Exercise 4

```{r quiz1, echo=FALSE}
  question("What the function to import tables? (select ALL that apply)",
    answer("read.table", correct = TRUE),
    answer("ggplot"),
    answer("read.csv", correct = TRUE),
    answer("read.delim", correct = TRUE),
    incorrect = "Incorrect. You're on Earth, in the Milky Way, at a computer."
  )
```

## Package ggplot2

### Exercise 5

```{r question_checkbox, echo=FALSE}
question_checkbox(
"Select all the toppings that belong on a package ggplot2:",
answer("theme", correct = TRUE),
answer("ggplot", correct = TRUE),
answer("geom", correct = TRUE),
answer("aes", correct = TRUE),
answer("plot", message = "This function create basic graphics in R"),
answer("tibble"),
answer("rmarkdown"),
answer("rnorm"),
random_answer_order = TRUE,
allow_retry = TRUE,
try_again = "Be sure to select all four toppings!"
)
```

## Tutorial video

![](https://www.youtube.com/watch?v=-uwJOuAg-JY)